\section{IMPLEMENTATION}
Implementing a Co-operative Society Management System involves creating a software 
application that helps manage the various activities and operations of a Co-operative society. 
Here's a basic outline of how you can implement such a system:

\subsection{Dashboard:}
At a glance, show approved, rejected, pending, and waiting societies. It also displays system services based on user roles.

\subsection{Society Management:}
\begin{itemize}
    \item Add and edit societies with documents in this screen by the entry user.
    \item Post to verify user follows up on his activities management and checks information and documents.
    \item Society data on the field is then submitted to the approval user.
    \item Approval user approves the society, then a 19-digit code (Example: 2023.1.01.4161.0001) is generated and stored in the society main table (\texttt{samity\_info}).
\end{itemize}

\subsection{Members Management:}
\begin{itemize}
    \item Two types of entry processes: entry system and excel file upload for approved societies.
    \item Generate an ID for member code and store it in the \texttt{member\_info} table with a relational \texttt{samity\_id}.
\end{itemize}

\subsection{Committee Management:}
\begin{itemize}
    \item Three types of committee types: 
    \begin{enumerate}
        \item Approved First Committee (6-12 members) with a time duration of 2 years.
        \item Elected Committee (6-12 members) with a time duration of 3 years.
        \item Election Committee (3 members) with a time duration of 90 days.
        \item Interim Committee (3 selected members) with a time duration of 45 days.
    \end{enumerate}
    \item Present committee roles as per rules. All data stored in the \texttt{committee\_info} table.
\end{itemize}

\subsection{Website Setup:}
Every society gets one website for society information for Co-operative/Normal users. Set up includes Home, About Us, Members, Services, Project, and Contact of society.

\subsection{Reporting:}
Generate reports on society information, member information, committee information, and overall society performance. Detailed information report attributes link to Jasper Report.

% //////////////////////////////

\section{Implementation Tools}
\subsection{React Framework Next.js}
The "React Framework Next.js" is a powerful combination of two JavaScript technologies: React and Next.js. Here are some key features and benefits of using the React Framework Next.js:
\begin{itemize}
    \item Server-Side Rendering (SSR)
    \item Routing
    \item Automatic Code Splitting
    \item API Routes
    \item Built-in CSS Support
\end{itemize}

\subsection{Material UI}
Material UI is an open-source library for building user interfaces in the React UI Framework.

\subsection{Node.js}
Node.js is a powerful and versatile open-source JavaScript runtime environment that allows developers to execute JavaScript code outside of a web browser.

\subsection{Express JS Server}
Express.js is required to serve and process user requests from a data source.

\subsection{PostgreSQL}
PostgreSQL is a database server that supports the standard structured query language.

\subsection{Jasper Reports}
Jasper Reports is an open-source Java reporting library that can be used to create interactive reports and generate high-quality print documents. It is widely used for formats including PDF, HTML, Excel, CSV, and more.


% ////////////////////////////

\section{System Requirements}

\subsection*{Hardware Requirements}
\begin{tabular}{|p{2.5cm}|p{2.5cm}|}
  \hline
  \textbf{Processor} & Core i3 \\
  \hline
  \textbf{RAM} & 4GB or more \\
  \hline
  \textbf{Hard Disk Space} & 2GB \\
  \hline
\end{tabular}


\subsection*{Software Requirements}
\begin{tabular}{|p{3.5cm}|p{3.5cm}|}
  \hline
  \textbf{Operating System} & Windows 2010 or higher \\
  \hline
  \textbf{Database} & PostgreSQL \\
  \hline
  \textbf{System Server} & Express JS \\
  \hline
  \textbf{Web Browser} & Edge, Chrome, Firefox \\
  \hline
  \textbf{Jasper Server} & For Jasper Reports \\
  \hline
  \textbf{For Bangla Fonts} & Nikosh, SolaimanLipi \\
  \hline
\end{tabular}


