\chapter{Discussion and Conclusion}

\section{Limitations of Co-operative Society Management Systems}
Co-operative society management systems, like any other systems, have their limitations. Here are some common limitations associated with Co-operative society management systems:

\begin{enumerate}
    \item \textbf{Limited Resources}
    
    \item \textbf{Technical Expertise}
    
    \item \textbf{Data Security Concerns}
    
    \item \textbf{Integration Challenges}
    
    \item \textbf{Limited Access to Technology}
    
    \item \textbf{Resistance to Change}
    
    \item \textbf{Maintenance and Upkeep}
    
    \item \textbf{Customization Needs}
    
    \item \textbf{Dependency on Vendors}
    
    \item \textbf{Legal and Regulatory Compliance}
\end{enumerate}

Addressing these limitations requires careful planning, adequate resources, and a willingness to adapt to new technologies and processes. Co-operative societies need to assess their unique needs and challenges to select and implement a management system that aligns with their objectives and resources.


\section{Future-Oriented Plan for Co-operative Society Management}

Creating a robust Co-operative society management system requires careful planning and consideration of various aspects. Here's a future-oriented plan to enhance the efficiency and effectiveness of a Co-operative society management system:

\begin{enumerate}
    \item \textbf{Digital Transformation}
    
    \item \textbf{Data Security and Privacy}
    
    \item \textbf{Member Engagement}
    
    \item \textbf{Financial Management}
    
    \item \textbf{Governance and Compliance}
    
    \item \textbf{Community Building}
    
    \item \textbf{Analytics and Reporting}
    
    \item \textbf{Continuous Improvement}
    
    \item \textbf{Disaster Preparedness}
    
    \item \textbf{Environmental Sustainability}
\end{enumerate}

By integrating these strategies, a Co-operative society can not only streamline its operations but also enhance member satisfaction, foster community engagement, and ensure long-term sustainability in an ever-changing future landscape.
 

\section{Conclusion}

The implementation of a Co-operative Society Management System can have several positive outcomes for both the society and its members.

In conclusion, a Co-operative Society Management System not only modernizes the functioning of the society but also enhances member satisfaction, financial stability, and community development. It is a strategic investment that can pave the way for the sustainable growth of Cooperative societies in the future.



% referance //////////////////////////////////////////

\begin{thebibliography}{9}

    \bibitem{WalesCC}
    Wales Cooperative Centre. Available at \url{http://www.walescooperative.org/co-operative-movement}, last accessed on 17/09/2023.
    
    \bibitem{Lennoxtown}
    welcometolennoxtown.co.uk. 
    
    \bibitem{Sampson1906}
    Sampson, F. A. (1906). \textit{Missouri Historical Review}. Editor, The state Historical Society of Missouri. Available at \url{http://archive.org/stream/missourihistoric01missuoft/missourihistoric01missuoft_djvu.txt}, last accessed on 16/09/2023.
    
    \bibitem{Rediff}
    pages.rediff.com.
    
    \bibitem{Infed}
    infed.org. ``Education in Robert Owen’s new society: the New Lanark institute and schools.'' Available at \url{http://infed.org/mobi/}, last accessed on 19/09/2023.
    
    \bibitem{Carrell2007}
    Carrell, S. (2007). ``Strik Rochdale from the record books. The Co-op began in Scotland.'' Available at \url{http://www.theguardian.com/business/2007/aug/07/retail.uknews}, last accessed on 18/09/2023.
    
    \bibitem{PreserveArticles}
    preservearticles.com. ``Essay on the history of Cooperative Movement in India.'' Available at \url{http://www.preservearticles.com/201105076374/essay-on-the-history-of-cooperative-movement-in-india.html}, last accessed on 12/08/2023.
    
    \bibitem{PunjabRevenue}
    punjabrevenue.nic.in.
    
    \bibitem{NCUA}
    National Credit Union Administration. ``A brief History of Credit Unions.'' Available at \url{http://www.ncua.gov/about/history/Pages/CUHistory.aspx}, last accessed on 03/08/2023.
    
    \bibitem{Scribd}
    scribd.com. ``Co-operative society, its expansion and future possibilities in the context of Bangladesh.'' [online]. Available at \url{http://www.scribd.com/doc/103555619/Co-operative-Society-in-Bangladesh}, [last accessed on 01/10/2023].
    
    \bibitem{SheikhHasina2010}
    Sheikh Hasina. (2010). In ``39th National Cooperative Day.'' Available at \url{http://www.coop.gov.bd/National_coop_day.htm}, last accessed on 05/07/2023.
    
    % Additional references
    \bibitem{CoopGovBD}
    Co-operative Society. Available at \url{https://coop.gov.bd/}, last accessed on 01/10/2023.
    
    \bibitem{SomityKeeper}
    Somite Keeper. Available at \url{https://somitykeeper.com/}, last accessed on 03/10/2023.
    
    \bibitem{MaterialUI}
    Material UI. Available at \url{https://mui.com/}, last accessed on 01/10/2023.
    
    \bibitem{NextJS}
    Next JS. Available at \url{https://nextjs.org/}, last accessed on 01/10/2023.
    
    \bibitem{NodeJS}
    Node JS. Available at \url{https://nodejs.org/en}, last accessed on 01/10/2023.
    
    \bibitem{JasperReport}
    Jasper Report. Available at \url{https://community.jaspersoft.com/}, last accessed on 05/10/2023.
    
    \bibitem{PostgreSQL}
    PostgreSQL. Available at \url{https://www.postgresqltutorial.com/}, last accessed on 08/09/2023.
    
    \end{thebibliography}
    
    